\chapter{\acrshort{vuca} and the Public Sector Market}
\label{ch:vucaandpublicsector}

\begin{itemize}
\item{Idea is take the (notities van de overheid) and distil the plans.}
\item{Take the background information of how the public sector in the Netherlands is organised (freedom of ... per governmental institutes. Law of Municipalities by Thorbecke }
\item{Take a couple of interviews to verify. Three inteviews for triangulation}
\begin{itemize}
	\item{Franc Weerwind. Mayor of Municipality of Almere (Municipality).}
	\item{Nathan Ducastel. Director of VNG Realisatie (Governmental Agency}
	\item{Maarten Hillenaar. Director of Centric Public Sector Solutions (ISV).}
\end{itemize}
\item{Create conclusion on this part.}
\end{itemize}

\begin{remark}
	Also take iBestuur into account!!!
\end{remark}

Statement of Franc Weerwind Mayor of Municipality of Almere:\\
Developments are too fast. The governments cannot follow it in this pace. The government needs the private sector to keep up with developments.\\
This needs certain collaboration instead of customer supplier relationship.\\
Pace of Stressors is increasing in time!.\\

\begin{remark}
	Use the i-Strategy for a summary \parencite{Digitaleoverheid}
\end{remark}

Themes relevant for the government for 2021 until 2025.

\begin{enumerate}
	\item{I in het hart}
	\item{Digitale weerbaarheid}
	\item{ICT-landschap}
	\item{Generieke voorzieningen}
	\item{Informatiehuishouding}
	\item{Data en Algoritmen}
	\item{I-vakmanschap}
	\item{Transparantie en inzicht}
	\item{I-besturing}
	\item{Markt en innovatie}
\end{enumerate}

\begin{remark}
	Add English translation (not replacement because of citation.)
\end{remark}