\appendix
\chapter{Research Log}
\label{app:researchlog}

%\begin{table}[!h]

%	\begin{center}
%		\begin{tabularx}{\textwidth}{@{}lX@{}}
%		\begin{longtable}{\textwidth}{@{}lX@{}}
%\begin{longtable}{| p{.20\textwidth} | p{.80\textwidth} |} 
\begin{longtable}{p{.10\textwidth}p{.90\textwidth}}
			\toprule
			\textbf{Date} & \textbf{What} \\ \midrule%
			\endhead%
			\hline
			\endfoot%
			24/11/21 & Initial research subject proposal to AMS.\\%
			25/11/21 & Initial research subject proposal sent to Hans Mulder \& Yuri Bobbert.\\%
			30/11/21 & First meeting with Hans Mulder to explore the subject.\\%
			12/02/21 & AMS Master Project Coaching.\\%
			10/03/21 & Second meeting with Hans Mulder. Definitive Area of Research selected. The success factors of EA for Business Agility/Resilience/antifragility.\\%
			11/03/21 & Elaborated with COO Centric Public Sector Solutions on antifragility.\\%
			14/03/21 & Started research on the concept of antifragility.\\%
			03/04/21 & One Pager on the concepts Enterprise Architecture, Public Sector, Independant Software Vendor, and Antifragility.\\%
			04/04/21 & Deskresearch on concept Antifragility\\%
			10/04/21 & Reading Taleb.\\%
			25/05/21 & Third meeting with Hans Mulder.\\%
			20/06/21 & Creating 5 pager. Sent 5 pager presentation for review to Hans Mulder, Dieneke Schouten, and Maarten Hillenaar. Promotor suggestion Roland Ettema, Martin Op 't Land, Bas van Gils or Hans Mulder. Sugested Hans Mulder as promotor with Edzo Botjes as co-promotor.\\%
			21/06/21 & Requested Maarten Hillenaar as Sponsor, Dieneke Schouten as Second Reader, Jan Ploeg as participant in Delphi, Christiaan Konstapel as interviewee.\\%
			24/06/21 & Presentation of the Five Pager at the Master Consultancy Coaching masterclass at AMS.\\%
			29/06/21 & Created the LaTeX skeleton.\\%
			06/07/21 & Meeting with Edzo Botjes to get acquainted. Edzo Botjes accepted co-promotorship. Definitive Promotor and Co-Promotor are known. Hans Mulder and Edzo Botjes.\\%
			07/07/21 & Setting up GitHub Environment for collaboration with (Co-)Promotor.\\%
			14/07/21 & Selected the appropriate License for the thesis. **CC BY-NC 4.0**\\%
			16/07/21 & Webinar Value from being resilient (Xebia/Edzo)\\%
			17/07/21 & Requested Sponsor in helping selecting the Delphi Group Participants. The network of Sponsor is extensive.\\%
			24/07/21 & Analysed Thesis of Edzo Botjes. Created literature administration based on template of Yuri Bobbert (Added unique Key/ID, Relevance of Titel, Abstract and Contents, bib\LaTeX citation key, notes field, and used search strings). Changed the license in a less restricted license **CC BY-SA 4.0**\\%
			01/08/21 & Analysed Thesis of Edzo Botjes. Snowballing from Thesis of Edzo Botjes. Administration on Literature to be read.\\%
			02/08/21 & Contact with research sponsor about invites for the Delphi Group. Contacted an academia for participation in the Delphi Group. Created ORCID, Zenodo, and Researchgate account. Sorted Literature. Searched for missing references with PaperPanda. Wrote little scribbles on Research methodology. Discussed participants from VNG-Realisatie (not that many candidates for the Delphi Group). Decided with Sponsor that VNG-Realisatie can be seen as a Municipality (VNG is the association of dutch municipalities).\\%
			03/08/21 & Worked on Literature approach, literature administration, and the Methodology (research infrastructure and tools).\\%
			04/08/21 & Worked on the literature administration and finished the methodology of the research infrastructure and tools. Moved text blocks from earlier reports into the thesis for refinement. Moved the literature to the public repository and moved copyright and disclosed materials to the private repository. Changed the \LaTeX template so that the paragraph indents are as they should be. Added multiple Cite in the chapter template as an example.\\%
			05/08/21 & Invited EA of a Municipality, and two academia to join the Delphi Group from which one academia and the EA already confirmed their participation. Added extra literature to be evaluated based on a mailing list of BiZZdesign (State of Enterprise Architecture, volume 2021). Added a conference article from EDOC on Architecture Principles for supporting large-scale agile transformations. This cloud give insights on how to use Principles in an transformation to Antifragile. Found this document through the ORCID of Henderik Proper (co-author of the book Architecure Principles.\\%
			06/08/21 & The second academia confirmed the participation in the Delphi Group. Wrote the template the sponsor can use to invite people for the Delphi Group. The template (Dutch) is stored in the administrative repository.\\%
			11/08/21 & Worked on literature study on vacation. Dropbox broke so had to pull to locally.\\%
			12/08/21 & Worked on literature study.\\%
			15/08/21 & Worked on literature study. More and more about CAS and Resilience. Not that much known on Antifragility yet. Still snowballing the current available Body of Knowledge.\\%
			31/08/21 & Organised a meeting with Promotor and Co-Promotor on the 9th of September 2021 at the Antwerp Management School from 11:30 until 13:30 before masterclasses about Agile Enterprise Architecture \& Enterprise Engineering.\\%
			01/09/21 & Meeting with Co-Promotor about being stuck in the literature study part of the research. Talked about narrowing the scope, defining important keywords and possible only searching for relevant literature after 2019 (study of Co-Promotor). Some new direction given from the Co-Promotor. He did not use the articles by Barry M. O'Reilly from the ANT conferences but it may be the right direction for the research.\\%
			03/09/21 & Research on the ANT conferences and pulled some relevant articles into the research. Administration of Literature study.\\%
			04/09/21 & Literature study. Read the articles of Barry M. O'Reilly. Shared the articles of Barry M. O'Reilly with colleagues responsible for Software Development and Architecture.\\%
			05/09/21 & Literature study and structure of thesis. Worked on the introduction and added some new relevant information to the theoretical background.\\%
			06/09/21 & Literature study.\\%
			08/09/21 & Administration and preparations for meeting with Promotor and Co-Promotor on the 9th of September at the AMS.\\%
			09/09/21 & Alignment with Co-Promotor and Promotor at the AMS. Administration on given answers. Requested the sponsor to take his place at the jury.\\%
			10/09/11 & Literature study.\\%
			15/09/21 & Visited the iBestuur congress for information on the public sector market and to network for the study/research.\\%
			16/09/21 & Literature study. Writing on Chapter 1 and 2.\\%
			19/09/21 & Writing on Chapter 1, 2 and 3. Refine email for sponsor for invitations of delphi group participants. Sponsor accepted his jury position.\\%
			20/09/21 & Finalising Chapter 1 for 10 pager AMS. Last refinement for Sponsor invitation email after meeting by telephone. \\ 
			21/09/21 & Wrote Barry O'Reilly an email with the request to meet and elaborate on the residuality theory.\\% 
			22/09/21 & Structuring and writing.\\%
			23/09/21 & Structuring and writing. Created a frozen release on GitHub of this release. Send the same compiled version of the thesis to the sponsor and the second reader.\\%
			24/08/21 & Master Project Coaching. Status update on Thesis.\\%
			\bottomrule %
%		\end{tabularx}
%		\label{tab:researchlog}
%	\end{center}
\end{longtable}