\chapter{Combined findings}
\label{app:combinedfindings}
We use this appendix to combine all the \glspl{attribute} with the three different qualitative research methods. In which research method were the \glspl{attribute} mentioned? The table knows multiple columns. The first column is the \gls{attribute} itself. The second column is if it was mentioned in literature, while the third column shows if it was was selected by the expert group. The final column shows the results of a scoring. In how many methods was the \gls{attribute} mentioned or selected.
{\small\tabcolsep=3pt  % hold it local
\begin{longtable}{@{}lllll@{}}
	\textbf{Attribute} & \rot{60}{\textbf{Literature}} & \rot{60}{\textbf{Interviews}} & \rot{60}{\textbf{Validation group}} & \rotatebox{60}{\textbf{Score (n out of 3)}} \\%
	\midrule%
	\endhead%
	\hline
	\multicolumn{5}{l}{* New attribute of the data set of the interviews.} \\%
	\multicolumn{5}{l}{** New attribute of the data set of the expert group.} \\%	
	\endfoot%
	\multicolumn{5}{l}{* New attribute of the data set of the interviews.} \\%
	\multicolumn{5}{l}{** New attribute of the data set of the expert group.} \\%	
	\caption[Possible success factors]{Possible success factors}
	\label{tab:possiblesuccessfactorstotal}
	\endlastfoot%
	\Gls{topdowncc} & \checkmark & & & 1 \\%
	\Gls{micromanagement} & \checkmark & & & 1 \\%
	\Gls{redundancy} & \checkmark & & & 1 \\%
	\Gls{modularity} & \checkmark & & & 1 \\%
	\Gls{looselycoupled} & \checkmark & & & 1 \\%
	\Gls{diversity} & \checkmark & & & 1 \\%
	\Gls{optionality} & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{nonmonotonicity} & \checkmark & \checkmark &  & 2 \\%
	\Gls{emergence} & \checkmark & & & 1 \\%
	\Gls{selforganisation} & \checkmark & \checkmark &  & 2 \\%
	\Gls{insertlowlevelstress} & \checkmark & & & 1 \\%
	\Gls{networkconnections} & \checkmark & & & 1 \\%
	\Gls{failfast} & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{resourcestoinvest} & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{senecabarbell} & \checkmark & \checkmark &  & 2 \\%
	\Gls{insertrandomness} & \checkmark & &  & 1 \\%		
	\Gls{reducenaiveintervention} & \checkmark & & & 1 \\%
	\Gls{skininthegame} & \checkmark & & & 1 \\%
	\Gls{personalmastery} & \checkmark & & & 1 \\%
	\Gls{sharedmentalmodel} & \checkmark & & & 1 \\%
	\Gls{buildingsharedvision} & \checkmark & & & 1 \\%
	\Gls{teamlearning} & \checkmark & & & 1 \\%
	\Gls{systemsthinking} & \checkmark & & & 1 \\%
	\Gls{safeworkingenvironment}\textsuperscript{*} & & \checkmark & \checkmark & 2 \\%
	\Gls{outsideincollaboration}\textsuperscript{**} & & & & \\%
	\Gls{datagovernanceplanes}\textsuperscript{**} & & & & \\%
	\Gls{systeminenvironment}  & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{holisticsystemicstance} & \checkmark & \checkmark &  & 2 \\%
	\Gls{organisationallearning} & \checkmark & \checkmark &  & 2 \\%
	\Gls{environmentallearning} & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{intraorganisationalcoherency} & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{systeminenvironmentcoevolutionlearning} & \checkmark & \checkmark & \checkmark & 3 \\%
	\Gls{adapttobusinesslanguage}\textsuperscript{*}  & & \checkmark & \checkmark & 2 \\%
	\Gls{agileenterprise}\textsuperscript{**} & & & & \\%
	\Gls{realtimetrust}\textsuperscript{**} & & & & \\%
	\Gls{fosterdialogue}\textsuperscript{**} & & & \checkmark & 1 \\%
	\Gls{architecturevalidation}\textsuperscript{**} & & & \checkmark & 1 \\%			
	\Gls{alwaysfittingarchitecture}\textsuperscript{**} & & & & \\%
	\bottomrule%
\end{longtable}%
}%