\chapter{Expert group}
\label{ch:expertgroup}
\setcounter{footnote}{0}
The \glspl{attribute}, as a result of the interviews (\cref{sec:attributeslikelysf}), are likely to have a positive influence on \acrlong{ea} in achieving \gls{antifragility} in the Dutch \gls{ps}. We used these \glspl{attribute} for validation by an expert group. All the expert group participants were selected to have experience with \acrlong{ea} and the Dutch \gls{ps}. The expert group was composed of experts from different organisations and organisational types of the Dutch \gls{ps}. A survey on experience with \acrlong{ea}, \gls{antifragility}, and the \gls{ps} was part of the expert group session (\cref{tab:experiencevalidationgroup}). Central governments, local governments, independent software vendors, service providers, and universities all had delegates in the expert group. A total of ten experts participated in an online session. 
 
The duration of the expert group session was two hours. The expert group session was online with support of Microsoft Teams and Meeting Wizard (a group support system). The session was recorded and automatically transcribed. All participants gave their consent for the recording and transcribing. The recording and transcription are not publicly available because they cannot be anonymised\footnote{The Antwerp Management School can request the recordings and transcriptions only for (re)accreditations and visitations to enable the Antwerp Management School to comply with statutory obligations. The recordings and transcriptions are kept for seven years after graduation before they are deleted.}.
\begin{longtable}{@{}p{.55\textwidth}ccc@{}}
	\toprule%
	\textbf{Question} & \textbf{Years} & \textbf{Variability} & \textbf{Abstains} \\
	\midrule%
	\endhead%
	\hline
	\endfoot%
	\caption[Average experience of expert group participants]{Average experience of expert group participants}
	\label{tab:experiencevalidationgroup}%
	\endlastfoot%
	How many years of experience do you have in the field of \acrlong{ea}? & 9,8 & 8\% & 0 \\%
	How many years have you worked as an (Enterprise) Architect? & 10,6 & 12\% & 0 \\%
	How many years of experience do you have in the field of complexity sciences (like \gls{antifragile})? & 7,4 & 16\% & 0 \\%
	How many years of experience do you have with the \gls{ps}? & 12,2 & 17\% & 0 \\%
	How many years of experience do you have with working in publicly-held organisations? & 10 & 16\% & 0 \\%
	How many years of experience do you have with working in privately-held organisations? & 17,2 & 21\% & 0 \\%
	\bottomrule%
\end{longtable}
All the participants received information beforehand. This information contained the invite, the goal of the session, the agenda and all relevant definitions. Three recorded seminars given by Nassim Nicholas Taleb\footnote{\url{https://youtu.be/B2-QCv-hChY}}\footnote{\url{https://youtu.be/1NXaafTpVjM}}\footnote{\url{https://youtu.be/C40zwpdc_yo}} were shared to ensure that the participants had a basic understanding of \gls{antifragility}. All participants confirmed that they did see at least one of the videos. The book of \textcite{Taleb2012} was read by multiple participants. We used the following agenda for the session:
\begin{enumerate}
	\item{Introduction}
	\item{Survey on the experience of the participants}
	\item{Presentation on the results of the research up to now\footnote{\url{https://github.com/JRBliekendaal/master-thesis/blob/3666f93bb95308572722082393e684ba40caa5cb/datasets/expertgroup/validationsession.pdf}}}
	\item{Validation of \glspl{attribute} \gls{antifragile}}
	\item{Validation of the \acrlong{ea} schools of thought and the \acrlong{ea} \glspl{attribute}l}
	\item{Survey on the relevance of the research}
\end{enumerate}
Meeting Wizard supported the surveys and validations. The data set of the surveys and validations is publicly available as a Microsoft Excel file in the public GitHub repository\footnote{\url{https://github.com/JRBliekendaal/master-thesis/blob/3666f93bb95308572722082393e684ba40caa5cb/datasets/expertgroup/dataset_expertgroup.xlsx}} of this research.
\section{Validation of attributes}
\label{sec:validationofattributes}
The two newly found attributes \textit{\gls{safeworkingenvironment}} and \textit{\gls{adapttobusinesslanguage}} (\cref{sec:attributeslikelysf}) were moved to the \gls{antifragile} \glspl{attribute} and \acrlong{ea} \glspl{attribute}. We used brainstorming to make sure that we did not miss possible \glspl{attribute} that are specific to the (Dutch) \gls{ps}. Through brainstorming as a group, the participants could add new \glspl{attribute}. The expert group explained, discussed, combined and sorted the added \glspl{attribute}. The participants rated the \glspl{attribute} one by one. They used a scale from one to ten, one for least likely and ten for most likely. There was a rating for the \glspl{attribute} of \gls{antifragility}, \acrlong{ea} and for the \acrlong{ea} schools of thought. The participants rated the \glspl{attribute} by answering the following questions:
\begin{enumerate}
	\item{For the \glspl{attribute}: ''To what extent is the \gls{attribute} a success factor for \gls{antifragility} in the \gls{ps}?''}
	\item{For the \acrlong{ea} schools of thought: ''To what extent is the \acrlong{ea} school of thought a success factor for \gls{antifragility} in the \gls{ps}?''}
\end{enumerate}
\subsection{Validation of antifragile attributes}
\label{sub:validationofantifragileattributes}
While brainstorming, the participants came up with twelve new \glspl{attribute}. After discussion, only two remained. These two were \textit{'\gls{outsideincollaboration}'} and \textit{'\gls{datagovernanceplanes}'}. The others were the same as another \gls{attribute} or were a child of one of the other \glspl{attribute}. The participants rated a total of nine \glspl{attribute}. As \cref{tab:validationofantifragileattributes} shows there are three \glspl{attribute} that had a variability of more than 40\%, and only two \glspl{attribute} scored less than a rating of six. The new \glspl{attribute} were among those. There was one abstain on three \glspl{attribute}. \Cref{sec:validationofafattributes} contains the details of the rating per \gls{attribute}.
\begin{table}[H]
	\centering
	\begin{tabular}{p{.55\textwidth}ccc}
		\toprule
		\textbf{Attribute} & \textbf{Rating} & \textbf{Variability} & \textbf{Abstains} \\
		\midrule
		\Gls{optionality} & 6,9 & 32\% & 0 \\%
		\Gls{nonmonotonicity} & 7 & 51\% & 0 \\%
		\Gls{selforganisation} & 8,2 & 23\% & 0 \\%
		\Gls{failfast} & 7,8 & 35\% & 0 \\%
		\Gls{resourcestoinvest} & 6,7 & 36\% & 1 \\%
		\Gls{senecabarbell} & 5,8 & 37\% & 1 \\%
		\Gls{safeworkingenvironment} & 7,4 & 31\% & 0 \\%
		\Gls{outsideincollaboration} & 6,2 & 55\% & 0 \\%
		\Gls{datagovernanceplanes} & 4,4 & 56\% & 1 \\%
		\bottomrule
	\end{tabular}%
	\caption{Validation of antifragile attributes}
	\label{tab:validationofantifragileattributes}%
\end{table}%

\subsection{Validation of Enterprise Architecture schools of thought}
\label{sub:validationofeaschools}
Validating the \acrlong{ea} schools of thought needed a somewhat different approach. The presentation\footnote{\url{https://github.com/JRBliekendaal/master-thesis/blob/3666f93bb95308572722082393e684ba40caa5cb/datasets/expertgroup/validationsession.pdf}} given to the expert group introduced the \glspl{attribute} of \gls{antifragile} and \acrshort{ea}. The expert group could extend the list of \glspl{attribute} with new \glspl{attribute} by brainstorming. There is a high chance of influencing the expert group when presenting the most likely \acrlong{ea} school of thought. The approach was to use the expert group to validate the findings in a non-biased way. Because of this, the validation used all three schools of thought. The expert group could rate the likelihood of the school of thought positively influencing \acrlong{ea} in achieving \gls{antifragility} in the Dutch \gls{ps}. 

The rating had low variability, and no abstains (\cref{tab:validationgscoreeaschools}). \textit{\gls{enterpriseitarchitecting}} had the lowest rating and \textit{\gls{enterpriseecologicaladaptation}} had the highest with \textit{\gls{enterpriseintegrating}} in between. The rating confirmed the results of the literature research (\cref{sub:definingea}) and the interviews (\cref{sec:dataprep}). \Cref{sec:validationofeaschools} contains the details of the rating per \acrlong{ea} school of tought.
\begin{table}[H]
	\centering
	\begin{tabular}{p{.55\textwidth}ccc}
		\toprule
		\textbf{School of thought} & \textbf{Rating} & \textbf{Variability} & \textbf{Abstains} \\
		\midrule%
		\Gls{enterpriseitarchitecting} & 5,6   & 34\%  & 0 \\
		\Gls{enterpriseintegrating} & 7,2   & 16\%  & 0 \\
		\Gls{enterpriseecologicaladaptation} & 8,8   & 27\%  & 0 \\
		\bottomrule%
	\end{tabular}%
	\caption[Rating of Enterprise Architecture schools of thought]{Rating of Enterprise Architecture schools of thought}
	\label{tab:validationgscoreeaschools}
\end{table}%
\subsection{Validation of Enterprise Architecture attributes}
\label{sub:validationofenterprisearchitectureattributes}
The validation of the \acrshort{ea} \glspl{attribute} used the same approach like that of the \gls{antifragile} \glspl{attribute}. The validation contained the \glspl{attribute} of the \acrlong{ea} school of thought of \gls{enterpriseecologicaladaptation}. Brainstorming resulted in nine new identified \glspl{attribute}. After discussion, five remained. These five were \textit{\gls{agileenterprise}}, \textit{\gls{realtimetrust}}, \textit{\gls{fosterdialogue}}, \textit{\gls{architecturevalidation}} and \textit{\gls{alwaysfittingarchitecture}}. The participants rated the \glspl{attribute}.

The rating shows that five \glspl{attribute} have a variability of 40\% or higher, and only one \gls{attribute} got a rating of less than six (\cref{tab:validationofeaattributes}). All three were from the five new \glspl{attribute} from the expert group. There were only two abstains on a total of two attributes. \Cref{sec:validationofeaattributes} contains the details of the rating per \gls{attribute}.
\begin{table}[H]
	\centering
	\begin{tabular}{p{.55\textwidth}ccc}
		\toprule
		\textbf{Attribute} & \textbf{Rating} & \textbf{Variability} & \textbf{Abstains} \\
		\midrule
		\Gls{systeminenvironment} & 7,7   & 28\%  & 0 \\
		\Gls{holisticsystemicstance} & 7     & 47\%  & 0 \\
		\Gls{organisationallearning} & 7,3   & 44\%  & 0 \\
		\Gls{environmentallearning} & 7,7   & 29\%  & 0 \\
		\Gls{intraorganisationalcoherency} & 6,4   & 31\%  & 0 \\
		\Gls{systeminenvironmentcoevolutionlearning} & 6,6   & 36\%  & 0 \\
		\Gls{adapttobusinesslanguage} & 7,1   & 35\%  & 0 \\
		\Gls{agileenterprise} & 6,4   & 50\%  & 0 \\
		\Gls{realtimetrust} & 5,6   & 54\%  & 1 \\
		\Gls{fosterdialogue} & 6,9   & 32\%  & 0 \\
		\Gls{architecturevalidation} & 7,4   & 24\%  & 0 \\
		\Gls{alwaysfittingarchitecture} & 5,8   & 46\%  & 1 \\
		\bottomrule
	\end{tabular}%
	\caption[Rating of Enterprise Architecture attributes]{Rating of Enterprise Architecture attributes}
	\label{tab:validationofeaattributes}%
\end{table}%

\section{Relevance of the research}
\label{sec:relevanceofresearch}
The final part of the expert group session was about the relevance of the research. A survey determined the research's relevance. The expert group rated the research on different areas of application. These areas of relevance were, \textit{in general}, \textit{for themselves}, \textit{for the public sector} and \textit{for the organisation of the expert}. The last question asked was if the expert group session fulfilled the expectations.

The variability of the ratings was low. There was only one abstain on the relevance of the research for the public sector. The question that scored the least was about the relevance for the organisation of the expert. The expert group finds the research relevant. They rated it with a rating of 8,2 (\cref{tab:relevanceofresearch}). \Cref{sec:relevanceofresearchandexpectations} contains the details of the rating per question.
\begin{table}[H]
	\centering
	\begin{tabular}{p{.55\textwidth}ccc}
		\toprule
		\textbf{Question} & \textbf{Rating} & \textbf{Variability} & \textbf{Abstains} \\
		\midrule
		To what extent do you find the research relevant? & 8,2 & 23\% & 0 \\%
		To what extent did this session fulfil your expectations? & 8 & 24\% & 0 \\%
		To what extent do you think that the research can be used by yourself? & 7,7 & 10\% & 0 \\%
		To what extent do you think that the research can be used in the public sector? & 7,2 & 32\% & 1 \\%
		To what extent do you think that the research can be used by your organisation? & 6,6 & 33\% & 0 \\%
		\bottomrule
	\end{tabular}%
	\caption[Rating of the relevance of the research]{Rating of the relevance of the research}
	\label{tab:relevanceofresearch}%
\end{table}%
\section{Attributes most likely to be a success factor}
\label{sec:expertattributessf}
The used research approach is a qualitative method. The number of participants was ten. We believe that n=10 is too small of a sample size to use pure quantitative tools. We decided not to use variability as a factor for selection. Instead, we are using a consensus model—the same as that of the interviews \cref{sec:dataprep}. With the interviews, we used the consensus model to determine that when 75\% of the interviews mentioned the \gls{attribute}, it could be an \gls{attribute} of any significance. For the results of the expert group, we decided to use the rule that at least 75\% of the experts must rate an \gls{attribute} a six or higher to be an attribute of any significance. We round down the 75\% sample size to a whole number. Abstains are not used in this calculation. We decided to use a rating of six because it is more than only half, it will make it even more probable that an attribute is of any significance.

\subsection{Selected antifragile attributes}
\label{sub:validationselectedafattributes}
Applying the rule for selection results in three dropped and six accepted \glspl{attribute} (\cref{tab:expertgrouppossiblesf}). The three dropped \glspl{attribute} are \gls{senecabarbell}, \gls{outsideincollaboration}, and \gls{datagovernanceplanes}. The accepted \glspl{attribute} are \gls{optionality}, \gls{nonmonotonicity}, \gls{selforganisation}, \gls{failfast}, \gls{resourcestoinvest}, and \gls{safeworkingenvironment}. None of the expert group's proposed \glspl{attribute} was selected. The rule dropped only one \gls{attribute} from the literature study, \gls{senecabarbell}.
\begin{longtable}{@{}lcccc@{}}
	\toprule%
	\textbf{Attribute} & \textbf{Votes} & \textbf{75\%} & \textbf{Votes $\geq$ 6} & \textbf{Selected} \\%
	\midrule%
	\endhead%
	\hline
	\endfoot%
	\caption[Identified antifragile attributes by the expert group]{Identified antifragile attributes by the expert group}
	\label{tab:expertgrouppossiblesf}
	\endlastfoot%
	\Gls{optionality} & 10 & 7 & 8 & \checkmark \\%
	\Gls{nonmonotonicity} & 10 & 7 & 8 & \checkmark \\%
	\Gls{selforganisation} & 10 & 7 & 10 & \checkmark \\%
	\Gls{failfast} & 10 & 7 & 9 & \checkmark \\%
	\Gls{resourcestoinvest} & 9 & 6 & 6 &  \checkmark\\%
	\Gls{senecabarbell} & 9 & 6 & 4 & \\%
	\Gls{safeworkingenvironment} & 10 & 7 & 9 & \checkmark \\%
	\Gls{outsideincollaboration} & 10 & 7 & 6 & \\%
	\Gls{datagovernanceplanes} & 9 & 6 & 3 & \\%
	\bottomrule%
\end{longtable}%

\subsection{Selected Enterprise Architecture attributes}
\label{sub:validationselectedeaattributes}
When we applied the same rule to the \glspl{attribute} of \acrlong{ea}, we have a result of three dropped attributes and nine \glspl{attribute} that are selected (\cref{tab:expertgrouppossiblesfea}). The three dropped \glspl{attribute} are \gls{agileenterprise}, \gls{realtimetrust}, and \gls{alwaysfittingarchitecture}. The nine selected attributes are \gls{systeminenvironment}, \gls{holisticsystemicstance}, \gls{organisationallearning}, \gls{environmentallearning}, \gls{intraorganisationalcoherency}, \gls{systeminenvironmentcoevolutionlearning}, \gls{adapttobusinesslanguage}, \gls{fosterdialogue}, and \gls{architecturevalidation}. Two out of five attributes that were proposed by the expert group are selected. \Gls{agileenterprise}, \gls{realtimetrust}, and \gls{alwaysfittingarchitecture} were dropped.
\begin{longtable}{@{}lcccc@{}}
	\toprule%
	\textbf{Attribute} & \textbf{Votes} & \textbf{75\%} & \textbf{Votes $\geq$ 6} & \textbf{Selected} \\%
	\midrule%
	\endhead%
	\hline
	\endfoot%
	\caption[Identified Enterprise Architecture attributes by the expert group]{Identified Enterprise Architecture attributes by the expert group}
	\label{tab:expertgrouppossiblesfea}
	\endlastfoot%
	\Gls{systeminenvironment} & 10 & 7 & 9 & \checkmark  \\%
	\Gls{holisticsystemicstance} & 10 & 7 & 8 & \checkmark \\%
	\Gls{organisationallearning}  & 10 & 7 & 9 & \checkmark \\%
	\Gls{environmentallearning} & 10 & 7 & 9 & \checkmark \\%
	\Gls{intraorganisationalcoherency} & 10 & 7 & 8 & \checkmark \\%
	\Gls{systeminenvironmentcoevolutionlearning} & 10 & 7 & 8 & \checkmark \\%
	\Gls{adapttobusinesslanguage} & 10 & 7 & 8 & \checkmark \\%
	\Gls{agileenterprise} & 10 & 7 & 6 & \\%
	\Gls{realtimetrust} & 9 & 6 & 5 & \\%
	\Gls{fosterdialogue} & 10 & 7 & 8 & \checkmark \\%
	\Gls{architecturevalidation} & 10 & 7 & 9 & \checkmark \\%
	\Gls{alwaysfittingarchitecture} & 9 & 6 & 5 & \\%
	\bottomrule%
\end{longtable}%

\subsection{Selected attributes as possible success factors}
\label{sub:validationselectedattributesassf}
Combining both sets (\cref{tab:expertgrouppossiblesf,tab:expertgrouppossiblesfea}) gives an overview. This overview summarises the \glspl{attribute} that are rated best by the expert group (\cref{tab:expertgroupp2ossiblesf}). These \glspl{attribute} can be significant in achieving \gls{antifragility} with \acrlong{ea} in the Dutch \gls{ps}. The set contains fifteen \gls{attribute}. Six \gls{antifragile} \glspl{attribute} from which one new discovered \gls{attribute}. Furthermore, nine \acrlong{ea} \glspl{attribute} from which two new discovered \glspl{attribute}.
\begin{longtable}{@{}ll@{}}
	\toprule%
	\textbf{Attribute} & \textbf{Category}  \\%
	\midrule%
	\endhead%
	\hline
	\endfoot%
	\caption[Possible success factors identified by the expert group]{Possible success factors identified by the expert group}
	\label{tab:expertgroupp2ossiblesf}
	\endlastfoot%
	\Gls{optionality} & \Gls{antifragile} \\%
	\Gls{nonmonotonicity} & \Gls{antifragile} \\%
	\Gls{selforganisation} & \Gls{antifragile} \\%
	\Gls{failfast} & \Gls{antifragile} \\%
	\Gls{resourcestoinvest} & \Gls{antifragile} \\%
	\Gls{safeworkingenvironment} & New \Gls{antifragile} \\%
	\Gls{systeminenvironment} & \acrlong{ea} \\%
	\Gls{holisticsystemicstance} & \acrlong{ea} \\%
	\Gls{organisationallearning} & \acrlong{ea} \\%
	\Gls{environmentallearning} & \acrlong{ea} \\%
	\Gls{intraorganisationalcoherency} & \acrlong{ea} \\%
	\Gls{systeminenvironmentcoevolutionlearning} & \acrlong{ea} \\%
	\Gls{adapttobusinesslanguage} & \acrlong{ea} \\%
	\Gls{fosterdialogue} & New \acrlong{ea} \\%
	\Gls{architecturevalidation} & New \acrlong{ea} \\%
	\bottomrule%
\end{longtable}%