% Glossary
\newglossaryentry{ps}
{
	name={public sector},
	description={The Public Sector is comprised of organisations that are owned and operated by the government and exist to provide services for its citizens.}
}
\newglossaryentry{artefact}
{
	name={artefact},
	plural={artefacts},
	description={description}
}
\newglossaryentry{agile}
{
	name=agile,
	plural={agility},
	description={The ability to adjust before failure happens}
}
\newglossaryentry{agility}
{
	name={agility},
	description={The state of being agile}
}
\newglossaryentry{antifragile}
{
	name=antifragile,
	plural={antifragility},
	description={The ability to strive for and evolve under stress}
}
\newglossaryentry{antifragility}
{
	name={antifragility},
	description={The state of being antifragile}
}
\newglossaryentry{fragile}
{
	name=fragile,
	plural={fragility},
	description={The quality of being easily broken or destroyed}
}
\newglossaryentry{fragility}
{
	name={fragility},
	description={The state of being fragile}
}
\newglossaryentry{resilient}
{
	name=resilient,
	plural={resiliency},
	description={The ability to recover from failure}
}
\newglossaryentry{resiliency}
{
	name={resiliency},
	description={The state of being resilient}
}
\newglossaryentry{robust}
{
	name=robust,
	plural={robustness},
	description={The ability to resist failure}
}
\newglossaryentry{robustness}
{
	name={robustness},
	description={The state of being robust}
}
\newglossaryentry{volatile}
{
	name=volatile,
	description={Likely to change in a very sudden or extreme way}
}
\newglossaryentry{uncertain}
{
	name=uncertain,
	description={Not known beyond doubt}
}
\newglossaryentry{uncertainty}{
	name={uncertainty},
	description={the state of being uncertain}
}
\newglossaryentry{complex}
{
	name=complex,
	description={A whole made up of complicated or interrelated parts}
}
\newglossaryentry{ambiguous}
{
	name=ambiguous,
	description={Not expressed or understood clearly}
}
\newglossaryentry{stressor}
{
	name={stressor},
	description={An event from outside the system that causes stress}
}
\newglossaryentry{glos_fmea}
{
	name={Failure Mode Effects Analysis},
	description={Is a Six Sigma technique that helps manage quality in a system by investigating how the system will cope with failure}
}
\newglossaryentry{entropy}
{
	name={entropy},
	description={The entropy of the universe increases in all natural processes. Isolated systems tend towards greater disorder and entropy is a measure of that disorder}
}
\newglossaryentry{digitaltransformation}{
	name={digital transformation},
	description={Digital Transformation is the application of digital capabilities to processes, products, and assets to improve efficiency, enhance customer value, manage risk, and uncover new monetisation opportunities.}
}
\newglossaryentry{archframework}{
	name={architecture framework},
	description={An enterprise architecture framework (EA framework) defines how to create and use an enterprise architecture. An architecture framework provides principles and practices for creating and using the architecture description of a system. It structures architects' thinking by dividing the architecture description into domains, layers, or views.}
}
\newglossaryentry{immemorial}{
	name={immemorial},
	description={Reaching beyond the limits of memory, tradition, or recorded history}
}
\newglossaryentry{disintermediation}{
	name={disintermediation},
	description={Disintermediation is the process of cutting out one or more middlemen from a transaction, supply chain, or decision-making process}
}
\newglossaryentry{arduous}{
	name={arduous},
	description={Hard to accomplish or achieve}
}
\newglossaryentry{domain}{
	name={domain},
	plural={domains},
	description={A field of action, thought, influence, etc.: The Domain of Science}
}
\newglossaryentry{convex}{
	name={convex},
	description={Being a continuous function or part of a continuous function with the property that a line joining any two points on its graph lies on or above the graph. In the antifragile theory more upside than downside}
}
\newglossaryentry{concave}{
	name={cavex},
	description={Being a continuous function or part of a continuous function with the property that a line joining any two points on its graph lies below the graph. In the antifragile theory more downside than upside}
}
\newglossaryentry{personalmastery}{
	name={personal Mastery},
	description={Personal mastery is a discipline of continually clarifying and deepening our personal vision, of focusing our energies, of developing patience, and of seeing reality objectively}
}
\newglossaryentry{sharedmentalmodels}{
	name={shared mental models},
	description={Mental models are deeply ingrained assumptions, generalizations, or even pictures of images that influence how we understand the world and how we take action}
}
\newglossaryentry{buildingsharedvision}{
	name={building shared vision},
	description={A practice of unearthing shared pictures of the future that foster genuine commitment and enrollment rather than compliance}
}
\newglossaryentry{teamlearning}{
	name={team learning},
	description={Team learning starts with 'dialogue', the capacity of members of a team to suspend assumptions and enter into genuine 'thinking together'}
}
\newglossaryentry{systemsthinking}{
	name={systems thinking},
	description={The Fifth Discipline of Senge that integrates personal mastery, shared mental models, building shared vision, and team learning}
}
\newglossaryentry{attenuatevariety}{
	name={attenuate variety},
	description={Dampening or reducing the possible outcomes / states. A light that can be turned on and off has the variety of 2. Your hand during Rock, paper, scissors has the variety or 3}
}
\newglossaryentry{amplifyvariety}{
	name={amplify variety},
	description={Amplifying or increasing the possible outcomes / states. A light that can be turned on and off has the variety of 2. Introducing the possibility of setting the light intensity increases the possible states}
}
\newglossaryentry{resourcestoinvest}{
	name={resources to invest},	
	description={Oportonies can only be seized when there are resources free to do see. This can be money but also time and labour. To Survive a black swan investment should be possible}
}
\newglossaryentry{senecabarbell}{
	name={seneca's barbell},	
	description={To be antifragile you need a robust sub-system to which 80\%/90\% predictable value with low risk is situated. The 20\%/10\% should be used for high return on investment activities}
}
\newglossaryentry{insertrandomness}{
	name={insert randomness},	
	description={When insert-low-level stress and fail fails delivers no issues the next step is to insert randomness into the systems. A great example of this is Chaos Engineering by Netflix or the HackerOne bug-bounty system}
}
\newglossaryentry{reducenaiveintervention}{
	name={reduce naive intervention},	
	description={Intervention based on a model and reductionistic logic and ignoring the experience. An example is not listening to the experienced but not so articulate employee, or by ignoring the balance nature has found in a ecosystem}
}
\newglossaryentry{skininthegame}{
	name={skin in the game},	
	description={Make certain that the one making the decision and doing the work has a pain and gain relation with the outcome. This goes beyond having a feedback system in place. This is goed beyond having KPI’s in place. An example is that when working Agile scrum, the product owner should be a co-worker in the team for whom the solution is being build}
}
\newglossaryentry{topdowncc}{
	name={Top-Down Command \& Control},
	description={Top-Down command and control is in an organisation that a employee is not free to decide to go left or right but has to follow orders. The careful design of an iPhone or a good pen is also an example of limited freedom of movement in the product itself}
}
\newglossaryentry{micromanagement}{
	name={micromanagement},
	description={Micro-management is about the freedom in the use of the product. When there are minitious working instructions available in a business process the employee has no freedom in the execution of the job. Another great example is a lego building block. It is engineered and fabricated into the greatest detail creating a building block that is almost completely robust. Lego has a very small resilience behaviour through engineering}
}
\newglossaryentry{redundancy}{
	name={redundancy},
	description={Redundancy is about having not a single point of failure by making use of duplication. An example is a backup electricity generators. Another example is local government as backup system of the central government}
}
\newglossaryentry{modularity}{
	name={modularity},
	description={Modularity is the degree that components may be separated and recombined, often with the benefit of flexibility. For example the finance team and the marketing team. Another example is the user-interface module and the data storage module}
}
\newglossaryentry{loosely coupled}{
	name={loosely coupled},
	description={Loosely coupled is the degree of dependency on the exact working of another module. For example when the color-schema of a website is changed it is preferred that this does not impact the functioning of the website. Another example is that when there are new employees introduced at the finance department the taste of the coffee changes. It is important to understand that there is always some degree of coupling}
}
\newglossaryentry{diversity}{
	name={diversity},
	description={Diversity is internally not being a mono-culture and externally having options. For example having two different coffee suppliers. Or having a diverse team}
}
\newglossaryentry{optionality}{
	name={optionality},
	description={Optionality is an idea advanced by Nassim Taleb in his book Antifragile. At the most basic level, optionality just means having lots of options. If you develop a skill with many possible job opportunities, you have more optionality than someone who develops a skill that only has one or two job opportunities}
}
\newglossaryentry{nonmonotonicity}{
	name={non-monotonicity},
	description={Non-monotonicity is about not only learning from the good but als from the bad. For example the lessons learned during a retrospective session}
}
\newglossaryentry{emergence}{
	name={emergence},
	description={Emergence refers to the existence or formation of collective behaviors, what parts of a system do together that they would not do alone}
}
\newglossaryentry{selforganisation}{
	name={self organisation},
	description={Self-Organisation is a process where some form of overall order arises from local interactions between parts of an initially disordered system. For example students sitting together in the school cafeteria}
}
\newglossaryentry{insertlowlevelstress}{
	name={insert low-level stress},
	description={Continuous Improvement is achieved by inserting low-level of stress continuously into a learning system. This will keep the system sharp all the time}
}
\newglossaryentry{networkconnections}{
	name={network-connections},
	description={A network is created by connections to other nodes. More connections increases potential for optionality for new constructions and also new functionalities}
}
\newglossaryentry{failfast}{
	name={fail fast},
	description={The attributes ''diversity'', ''non-monotonicity'', ''emergence'', ''self-organisation'', ''insert low-level stress'', and ''network-connections'' combined enables the possibility to execute the strategy to embrace the adagium ''Fail Fast''.}
}
\newglossaryentry{foster}{
	name={foster},
	description={To promote the growth or development of}
}
\newglossaryentry{parliamentaryinquiry}{
	name={parliamentary inquiry},
	plural={parliamentary inquiries},
	description={The parliamentary committee of inquiry is a particular type of temporary committee of the House. The parliamentary inquiry is the most powerful instrument the Dutch parliament has at its disposal to carry out its duty to scrutinize the work of the government}
}
\newglossaryentry{houseofthorbecke}{
	name={the House of Thorbecke},
	description={In 1848, as minister, Thorbecke laid the foundations for the current administrative division and task demarcation. In 1850 and 1851 he established the Provinces Act and the Municipalities Act. We therefore also speak of 'the House of Thorbecke'}
}